---
title: "US Historical Transportation Data"
author: "Jacob Margolis"
date: "9/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r}
library("readxl")
#install.packages("ggplot2")
library(ggplot2)
library(dplyr)
```

```{r}
setwd("D:/R Project/US Intercity Transportation Dashboard")
```

## Import Data

* US Rail Passengers 2000-2020
```{r}
   
  SeasonalData_Rail_2000 <- read_xlsx("Rail_2000_2020.xlsx", 
                                     col_names = TRUE,
                                     range = cell_rows(1:246)) %>% 
  mutate(OBS_DATE = as.Date(OBS_DATE)) %>%
  mutate(OBS_DATE = format.Date(OBS_DATE, '%m/%Y'))
```
  
    + Notes
      - OBS_DATE = Observation Date		
      - RAIL_PM = Rail passenger miles		
      - RAIL_PM_D11 = Seasonally-adjusted rail passenger miles		
  
    + Data Source
      - Rail passenger miles - U.S. Department of Transportation Federal Railroad Administration available at: http://safetydata.fra.dot.gov/OfficeofSafety/ 
      - Seasonally-adjusted rail passenger miles - U.S. Department of Transportation of Transportation Statistics (BTS) calculation from data collected by U.S. Department of Transportation, Federal Railroad Administration available at: http://safetydata.fra.dot.gov/OfficeofSafety/



##Graph

```{r}
chart <- ggplot(SeasonalData_Rail_2000, aes(x=OBS_DATE, y=RAIL_PM)) + 
  geom_line() +
  labs(x = "Date", y = "Passengers")+
  scale_x_date(limits = c("01/2020", "04/2020"),
                 date_breaks = "3 year")
chart

```