---
title: "US Historical Transportation Data"
author: "Jacob Margolis"
date: "9/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r}
#install.packages("read_xls")
#install.packages("ggplot2")
library(base)
library(stats)
library(readr)
library(ggplot2)
library(dplyr)
#library(lubridate)
```

```{r}
# setwd("D:/R Project/US Intercity Transportation Methods Dashboard")
setwd(file.path("D:", "R Project", "US Intercity Transportation Dashboard"))
```

## Import Data

* US Rail Passengers 2000-2020
```{r}
  
  SeasonalData_Rail_2000 <- read_csv("D:/R Project/US Intercity Transportation Dashboard/TransData.csv", 
  + col_types = cols(OBS_DATE = col_character()))
  #mutate(OBS_DATE = as.Date(OBS_DATE))  %>%
  #mutate(OBS_DATE = ymd(OBS_DATE))  # Using ymd from lubridate seems to be putting data into the correct format.
View(SeasonalData_Rail_2000)

```
  
    + Notes
      - OBS_DATE = Observation Date		
      - RAIL_PM = Rail passenger miles		
      - RAIL_PM_D11 = Seasonally-adjusted rail passenger miles		
  
    + Data Source
      - Rail passenger miles - U.S. Department of Transportation Federal Railroad Administration available at: http://safetydata.fra.dot.gov/OfficeofSafety/ 
      - Seasonally-adjusted rail passenger miles - U.S. Department of Transportation of Transportation Statistics (BTS) calculation from data collected by U.S. Department of Transportation, Federal Railroad Administration available at: http://safetydata.fra.dot.gov/OfficeofSafety/


 
##Graph

```{r}
chart <- ggplot(SeasonalData_Rail_2000, aes(x=OBS_DATE, y=RAIL_PM)) +
  geom_line() +
  labs(x = "Date", y = "Passengers") #+
 # scale_x_date(limits = c("01-01-2020", "04-01-2020"), date_breaks = "3 year") # it's unclear why scale_x_date is not working.  
chart

```